Improved Bounds for Online Balanced Repartitioning

### 2020-03-28 paper/paper.tex
LB comments

\maciek{TODO: better introduction of the concept of components IN THE LOWER BOUND. Perhaps other name than components to avoid confusion. Plus Figure.}

>>>>

\maciek{TODO: better introduction of the concept of adversary's components in the lower bound. Perhaps other name than adversary components to avoid confusion.}

\maciek{Rename components in this section to adversary's components. Until the better name is figured out.}

\maciek{Example figure of the construction and growing components.}
